One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-07-17 manuscript/manuscript.tex
Adding text to example sections

>>>>

To replicate this example case, build the code with the \texttt{CHEMISTRY = SIMPLEDLR} flag in the \texttt{user\textunderscore config} file and edit the desired run script with \texttt{inputDir = "../input/jetFlame/DLR\textunderscore A"} and a new case name such as \texttt{caseName = "jetFlame\textunderscore example"}. The input file for this case, located at \texttt{ODT/input/jetFlame/DLR\textunderscore A/input.yaml}, already contains the appropriate parameters and does not need to be modified to match this example case. POST PROCESSING INSTRUCTIONS GO HERE.
